---
title: "Four Parameters: Categorical"
author: "Anna Shao"
format: html
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false
library(primer.data)
library(tidyverse)
library(tidybayes)
library(brms)
library(gtsummary)
```

```{r}
#| label: cleaning
#| message: false
nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot",
  ))
```

```{r}
#| label: model
#| cache: true
fit_nes <- brm(formula = pres_vote ~ sex,
               data = nes_92,
               family = categorical(),
               silent = 2,
               refresh = 0,
               seed = 76)
```

```{r}
#| label: plot
#| warning: false
fit_nes |>
  add_epred_draws(newdata = tibble(sex = c("Female", "Male"))) |>
  select(sex, .category, .epred) |>
  ggplot(aes(x = .epred, fill = sex)) +
    geom_histogram(bins = 100) +
    facet_grid(~ .category) +
    scale_x_continuous(breaks = c(0.05, 0.3, 0.6),
                       labels = scales::percent_format()) +
    labs(title = "Posterior for Expected Probability of Candidate Support Among Women",
         subtitle = "Women are most likely to support Clinton",
         x = "Posterior Probability of Expected Vote Probability",
         y = "Count",
         fill = "Sex")
```
With data from the National Election Survey, we are trying to understand the relationship between voter preference of the top 3 candidates and sex in the 1992 Presidential election. However, stability may not hold because voters voted at different times, even in the fall of 1992. We created a categorical, multinomial logistic regression model with sex predicting voter preference. We found that male voters were negatively related with Clinton, suggesting that male voters were less likely to vote for Clinton. Overall, Women were more likely to vote for Clinton while men were more likely to vote for Perot. Expected percentage of votes for Bush were similar for women and men, with similar amounts of variability.

\begin{aligned}
\rho_{clinton} &=& \frac{e^{\beta_{0, clinton} + \beta_{1, clinton} male}}{1 + e^{\beta_{0, clinton} + \beta_{1, clinton} male}}\\
\rho_{perot} &=& \frac{e^{\beta_{0, perot} + \beta_{1, perot} male}}{1 + e^{\beta_{0, perot} + \beta_{1, perot} male}}\\
\rho_{bush}  &=& 1 - \rho_{clinton} - \rho_{perot}
\end{aligned}

```{r}
#| label: table
#| warning: false
tbl_regression(fit_nes)
```
